### 2021-10-12 README.Rmd
even more repo updates

@@

>>>>

Contains code used to produce figures for manuscript.

@@

Processed results files referenced in figure code `lowout.csv`, `medout.csv`, and `highout.csv` are quite large and are available upon request. `Processed csvs` contains posterior medians for all converged model runs. `row_-` files contains estimates of population trend, $\lambda$, where "-" is "low", "med", or "high" and corresponds to a decreasing, stable, or increasing population trend, respectively.
